Niche complementarity among pollinators increases community-level plant reproductive success

### 2020-04-30 Network_structure_and_function.Rmd
changes to include contribution to nestedness

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig. S1). Sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors. We surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed every two weeks for a total of 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers. Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and another expert entomologist (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly. Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per transect which makes 40m2 of area surveyed overall.

@@

  To evaluate differences in network structure between communities, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species. For each network, we extracted a series of relevant network metrics at the species and site levels.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness. 
 Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016]. As a measure of centrality, we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009]. With this method, links between plant species represent shared pollinator species.

@@

At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, and the average fruit weight fitted using normal distributions. The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories. As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species. Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats per transect. In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality. For both models, we included plant species identity nested within site and site as random effects to account for multiple individuals of the same plant species measured at each site.

@@

m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
summary(m0)

m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
summary(m1)
vif(m1)  #check for correlations between variables included in model

m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)

@@

AICtab(m0,m1, m2)

@@

m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=TRUE)

summary(m2)

r2<-rsquared(c(m2, m1)) #check R^2 values for both models

# extract estimates and st errors to present in table
coefs.m2 <- data.frame(coef(summary(m2)))
#coefs.m2
Table1A<-round(coefs.m2[,1:3],digits=2)
rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
#at the end of the paper

@@

y_partial_weigh <- remef(m2, fix= c( "rel.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv<-exp(y_partial_weigh)/(1+exp(y_partial_weigh))

Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
  stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
  xlab("Centrality") +      
  ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))

@@

y_partial_weigh2 <- remef(m2, fix= c( "weigh_closeness.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv2<-exp(y_partial_weigh2)/(1+exp(y_partial_weigh2))

FigureS5<-ggplot(m2@frame,  aes(x=m2@frame$rel.visits.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
  geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) +
  stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) +
  xlab("Relative number of visits") +
  ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) +
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))
#

#This relationship is largely driven by one single point species

#redo analysis removing one plant species with large number of visits

f2.sub<-subset(f2, f2$rel.visits.sc<4)

m2b<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.sub, REML=TRUE)

summary(m2b) #This relationship is largely driven by one single point species so we show results remving one species

# extract estimates and st errors to present in table
coefs.m2b <- data.frame(coef(summary(m2b)))
#coefs.m2
TableS5<-round(coefs.m2b[,1:3],digits=2)
rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
#at the end of the paper

@@

At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%). We found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig. 1A, Fig. S4). However, in the case of the relative number of visits a single point seemed to be driving the relationship and removing this single point lead to a decrease in the importance of this variable (Fig. S5, Table S5).

@@

s3$norm_degree<-outsp.pl.site$norm_degree[match(s3$match, outsp.pl.site$match)]
s3$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s3$match, outsp.pl.site$match)]
s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]

@@

s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
s3$rel.visits.sc<-scale(s3$rel.visits, center = T, scale = T)
s3$tot.visits.sc<-scale(s3$tot.visits, center = T, scale = T)

@@

s3$seedcomb<-s3$mean.seedn*s3$mean.seedw
s3$seedcomb.sc<-scale(s3$seedcomb, center = T, scale = T)

m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
summary(m0.seed)

m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)

@@

m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
summary(m2.seed)
vif(m2.seed)

AICtab(m0.seed, m1.seed, m2.seed) #m2 is best

m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=TRUE)
summary(m2.seed)

r2b<-rsquared(c(m2.seed, m1.seed)) #check R^2 values for both models

#test for problems in residuals
# res<-simulateResiduals(m2.seed)
# plot(res, rank = TRUE)

# extract estimates and st errors to present in table
coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
#coefs.m2.seed
Table1B<-round(coefs.m2.seed,digits=2)
rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")

#plot significant variables
y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "rel.visits.sc", "weigh_closeness.sc"), ran = "all")
#With this we remove the influece of x2 and the random effects from the dependent variable

Figure1b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Niche overlap") +      
  ylab("Number of \n seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))

#Figure1b

FigureS4<-plot_summs(m2, m2.seed, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds"), legend.title = "Response variables", cex.axis=2)

@@

 For the average number of seeds per fruit, our results showed again that model 2 had the best fit, with fixed effects explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data (conditional R^2 =`r round(r2b$Conditional[1], 2)*100`% ). In this case, we found a positive relationship between plant niche overlap and the number of seeds produced (Table 1B, Fig. 1B, Fig. S4).

@@

m0.seed.w<-glmer(mean.seedw ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)

summary(m0.seed.w)

m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)

summary(m1.seed.w)

m2.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)

summary(m2.seed.w)

AICtab(m0.seed.w, m1.seed.w, m2.seed.w)

#FRUIT WEIGHT
m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)

@@

m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)

@@

m2.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)

@@

```
 For fruit weight, none of the models fitted showed a better fit than the null model.

@@

FigureS6A<-plot_model(m2.fruit.net, title="Fruit set")
```

@@

FigureS6B<-plot_model(m2.seed.net, title="Number of seeds")
```

At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]). This suggests model 2 was a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only. Specifically, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig. 2, Fig. S6). Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig. 2, Fig. S6).

@@

#save table with results for paper
tableS6A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
rownames(tableS6A)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper

@@

FigureS7 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

#save table with results for paper
tableS6B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
rownames(tableS6B)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper

@@

FigureS8 <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

FigureS6C<-plot_model(m1.fruitw.net, title="Fruit weight")

@@

  In the case of fruit weight, we found that both the null model and model 1 were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]). Model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23. In this case, we found a positive link with site-level pollinator richness (Table S6A, Figs. S6-S7). This association was maintained even after removing a site that has a particularly large pollinator richness value (Table S6B, Fig. S8, Fig. S6).

@@

When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but none of the variables considered showed any strong associations (Table S8). In the case of the other two thresholds considered (25^th and 75^th percentiles) model 0, the null model, was the best model.

@@

  One of the unexpected results of our analyses is the strong negative relationship between total pollinator richness and fruit set at the site level. One possible explanation for this is that greater richness means greater transfer of heterospecific pollen [@Arceo-Gomez2019]. Another possible explanation to this might be the fact that pollinator richness includes all the pollinators recorded during our sampling efforts, i.e., it includes species that do not pollinate some of the species whose reproductive success was measured. More complex communities with more pollinators, but also with more plant species (Pearson correlation between plant and pollinator richness  = 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species. A way to reduce the competition exerted by these dominant species, which are precisely those evaluated in this study, is by reducing their reproductive success [@Lanuza2018; @Stavert2019]. These ideas open the door to exploring the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018]. In our case, while fruit set is negatively related to pollinator richness, it is important to note that fruit weight shows the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality. Thus, taking into account the densities of co-flowering plant species may be the next step [@Vanbergen2014].

@@

knitr::kable(list(Table1A, Table1B), caption = "**Table 1**. Results of GLMM showing the association between simple visitation and network structure metrics and A) species-level fruit set and B) average number of seeds per fruit based on best model selected. Bold letters indicate variables with large effects.")
```
\newpage

@@

**Figure 1**. Partial residual plots showing the effect of the single predictor which best explains the variability in species-level reproductive success. A) shows the effect of plant species centrality on the fruit set of each of the plant species considered and B) shows the effect of plant niche overlap on its average number of seeds per fruit. Dots represent each of the individuals sampled for each species within each site.

@@

FigureS5

```
**Figure S5.** Scatterplot showing the effect of the relative number of visits received by a focal plant on its reproductive success. Relationship is largely driven by one species with a particularly large value of relative visits and removing this point leads to no effect of visitation rate.

@@

FigureS6A
FigureS6B
FigureS6C

```
**Figure S6.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.

@@

FigureS8

>>>>

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig. S1). Sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), and similar habitat and soil types, reducing potential confounding factors. Similarity in plant composition between sites was `r round(d.betadiv, 2)` (plant mean Sørensen beta-diversity). We surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed every two weeks for a total of 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers. Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and another expert entomologist (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly. Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per transect which makes 40m2 of area surveyed overall.

@@

  To evaluate differences in network structure between communities, we constructed plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species. For each network, we extracted a series of relevant network metrics at the species and site levels.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, and (ii) the contribution to nestedness of each individual plant species. Niche overlap estimates the potential indirect interactions between plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019]. We calculated it as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016]. A plant species' contribution to nestedness is calculated by comparing the nestedness observed in a given community to that generated by randomizing the interactions in which a focal species is involved. Species that show important contributions to overall nestedness will have values >0, while species that do not contribute to overall nestedness wil show values <0 [@Saavedra2011].

@@

At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, and the average fruit weight fitted using normal distributions. The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories. As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species. Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats per transect. In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and contribution to nestedness. For both models, we included plant species identity nested within site and site as random effects to account for multiple individuals of the same plant species measured at each site.

@@

f2.na<-na.omit(f2[, c(1,13:14,25:28)]) #omit nas so analyses are done with exact same dataset

m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
summary(m0)

m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
summary(m1)
vif(m1)  #check for correlations between variables included in model

m2<-glmer(tot.fruitset ~ pollspsperplant.sc + rel.visits.sc  + niche.overlap.sc + nested_contribution.sc +   (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)

@@

AICtab(m0,m1, m2) #m2 is best model

stats::anova(m0,m1,m2) #compare model parsimony, quite similar

r2<-rsquared(c(m1, m2)) #check R^2 values for both models

@@

m2<-glmer(tot.fruitset ~   pollspsperplant.sc + rel.visits.sc  + niche.overlap.sc + nested_contribution.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=TRUE)
summary(m2)

#Anova(m2)

# extract estimates and st errors to present in table
coefs.m2 <- data.frame(coef(summary(m2)))
#coefs.m2
Table1A<-round(coefs.m2[,1:3],digits=2)
rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Plant niche overlap", "Contribution to nestedness")
#at the end of the paper

@@

y_partial_weigh <- remef(m2, fix= c("nested_contribution.sc", "rel.visits.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv<-exp(y_partial_weigh)/(1+exp(y_partial_weigh))

Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$pollspsperplant.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
  stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
  xlab("Pollinator richness") +      
  ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))

@@

y_partial_weigh2 <- remef(m2, fix= c("pollspsperplant.sc", "rel.visits.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv2<-exp(y_partial_weigh2)/(1+exp(y_partial_weigh2))

Figure1b<-ggplot(m2@frame,  aes(x=m2@frame$nested_contribution.sc, y=y_partial_weigh_inv2, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
  stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
  xlab("Contribution to nestedness") +      
  ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))

FigureS4<-plot_summs(m2, level=0.95, scale = TRUE, model.names = c("Fruit set"), legend.title = "Response variables", cex.axis=2)

@@

At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[2], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[2], 2)*100`%). We found a positive relationship between fruit set, pollinator species richness, and a network structure metric, the contribution to nestedness of a focal plant within the overall network (Table 1, Fig. 1, Fig. S4).

@@

s3$nested_contribution<-outsp.pl.site$nested_contribution[match(s3$match, outsp.pl.site$match)]
s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]

@@

s3$nested_contribution.sc<-scale(s3$nested_contribution, center = T, scale = T)
s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
s3$rel.visits.sc<-scale(s3$rel.visits, center = T, scale = T)
s3$tot.visits.sc<-scale(s3$tot.visits, center = T, scale = T)

@@

# s3$seedcomb<-s3$mean.seedn*s3$mean.seedw
# s3$seedcomb.sc<-scale(s3$seedcomb, center = T, scale = T)

s3.na<-na.omit(s3[,c(1:2,17:20,22)])

m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
summary(m0.seed)

m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)

@@

m2.seed<-glmer(mean.seedn.sc ~ pollspsperplant.sc  + rel.visits.sc +  niche.overlap.sc  + nested_contribution.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
summary(m2.seed)
vif(m2.seed)

AICtab(m0.seed, m1.seed, m2.seed) #m0 is best

stats::anova(m0.seed,m1.seed,m2.seed)

@@

@@

#FRUIT WEIGHT

s3.na2<-na.omit(s3[,c(1:2,6, 17:20)])

m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na2, REML=FALSE)

@@

m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na2, REML=FALSE)

@@

m2.fruit.w<-glmer(mean.fruitweight ~  nested_contribution.sc + niche.overlap.sc  +pollspsperplant.sc  + rel.visits.sc +  (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na2, REML=FALSE)

@@

```
For the average number of seeds per fruit at the species level as well as for fruit weight, our results showed that none of the models fitted were better than the null model explaining differences across plant species.

@@

FigureS5A<-plot_model(m2.fruit.net, title="Fruit set")
```

@@

FigureS5B<-plot_model(m2.seed.net, title="Number of seeds")
```

At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]). This suggests model 2 was a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only. Specifically, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig. 2, Fig. S5). Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig. 2, Fig. S5).

@@

#save table with results for paper
tableS5A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
rownames(tableS5A)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper

@@

FigureS6 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

#save table with results for paper
tableS5B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
rownames(tableS5B)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper

@@

FigureS7 <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

FigureS5C<-plot_model(m1.fruitw.net, title="Fruit weight")

@@

  In the case of fruit weight, we found that both the null model and model 1 were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]). Model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23. In this case, we found a positive link with site-level pollinator richness (Table S5A, Figs. S5-S6). This association was maintained even after removing a site that has a particularly large pollinator richness value (Table S5B, Fig. S7, Fig. S5).

@@

When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but none of the variables considered showed any strong associations (Table S6). In the case of the other two thresholds considered (25^th and 75^th percentiles) model 0, the null model, was the best model.

@@

  One of the unexpected results of our analyses is the strong negative relationship between total pollinator richness and fruit set at the site level. One possible explanation for this is that greater richness means greater transfer of heterospecific pollen [@Arceo-Gomez2019]. Another possible explanation to this might be the fact that pollinator richness includes all the pollinators recorded during our sampling efforts, i.e., it includes species that do not pollinate some of the species whose reproductive success was measured. More complex communities with more pollinators, but also with more plant species (Pearson correlation between plant and pollinator richness  = 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species. A way to reduce the competition exerted by these dominant species, which are precisely those evaluated in this study, is by reducing their reproductive success [@Lanuza2018; @Stavert2019]. These ideas open the door to exploring the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018]. In our case, while fruit set at the site level is negatively related to pollinator richness, it is important to note that fruit set at the species level and fruit weight show the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality. Thus, taking into account the densities of co-flowering plant species may be the next step [@Vanbergen2014].

@@

knitr::kable(list(Table1A), caption = "**Table 1**. Results of GLMM showing the association between simple visitation and network structure metrics and species-level fruit. Bold letters indicate variables with large effects (see Figure S4 for estimate confidence intervals).")
```
\newpage

@@

**Figure 1**. Partial residual plots showing the effect of A) pollinator species richness and B) the contribution to nestedness of each plant species on fruit set. Dots represent each of the individuals sampled for each species within each site.

@@

@@

FigureS5A
FigureS5B
FigureS5C

```
**Figure S5.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.

@@

FigureS7
